---
title: "ausvotesTR"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ausvotesTR)
```

`ausvotesTR` is an R package of the data provided by the Australian Electoral 
Commission's (AEC) [Transparency Register](https://transparency.aec.gov.au/).

The package aims to be both easier to access than the data on the AEC's 
website, and also to provide linkages and metadata that is available on the 
AEC site, but isn't readily accessed.

Scripts to re-create all of the data used in the package are included in 
the `data-raw` folder.

The package also contains some convenience functions for analysing the data
and a Shiny app for quickly searching for donations by donors.

## Installation

To install from GitLab:

```R
remotes::install_gitlab("damonism/ausvotesTR")
```

## Data extraction date

The [_Commonwealth Electoral Act 1918_](https://www.legislation.gov.au/Latest/C2019C00103) 
requires parties, associated entities, donors, third parties and political 
campaigners to submit an annual return with any donations above the
[disclosure threshold](https://www.aec.gov.au/Parties_and_Representatives/public_funding/threshold.htm) 
each financial year. Data extracted from the returns is then published on 
the first working day of the following February.

Regulated entities may submit an amendment to their returns to the AEC, and
the data in the package will reflect all of the returns and any amendments
at the time of extraction.

The current data in the package was extracted on `r format(returns_updated[1,1], "%d %B %Y")`.

## Disclosure threshold

The disclosure threshold is CPI indexed annually. Donations below
the threshold may not be included in returns.

The disclosure threshold for each year was:

```{r echo=FALSE, results='asis'}
library(knitr)
kable(disclosure_threshold(), format.args = list(big.mark = ','))
```

## Changelog

### 2 June 2021
- New data extract
- Added [package documentation](https://r-pkgs.org/man.html#man-packages) for
  the package (including adding a `globalVariables()` definition for the data
  frames so the package will pass a `devtools::check()` cleanly -- there must
  be a better way to do this with data packages!)
- bumped the version to 0.1.7

### 18 May 2021
- New data extract
- Renamed all of the search functions to makes them easier to find.
- Rolled `search_returns_date()` functionality into `search_returns()`.
- Fixed `search_returns()` so that even if it produces a nil return the
  columns are the correct format so you can join them with something like
  `map_dfr()` or `lapply()`.
- The scraper now uses `use_data()` from `usethis`, where it has moved from
  `devtools`. This is not reflected in dependencies as the scraper is not
  actually included in the package.
- A few documentation tweaks. 

### 14 March 2021
- `returns_search()` and associated functions no longer returns an error when
  there isn't a hit on the search (now returns a zero-row `data.frame` with
  all of the appropriate columns)

### 9 March 2021

- `returns_search()` is now case-insensitive, which seems to make more
  sense.

### 7 March 2021

- Fixed some documentation bugs so it now builds cleanly.
- Vignettes still not showing up -- not sure why.

### 2 February 2021

- Updated the data with the 2019-2020 returns
- Added summary tables to `transparency_register_scraper.R` in order to 
  provide some reassurance that the web scraping process continues to work
  properly (not yet complete for all tables)
- Bumped the version number to 0.1.5

### 16 December 2020

- Added this ReadMe
- Added `DisclosurePeriodEndDate` to `returns_receipts_details`, 
  `returns_donor_details`
- Implemented a more memory efficient way to standardise the `FinancialYear` 
  field
- Update the data
- Moved search functions from the Shiny app and exported them
- Updated version number to 0.1.4

## Todo
- [x] Combine `returns_search` and `returns_search_date`
- [ ] Add links to AEC returns from Shiny app
- [ ] Complete the documentation of the data
