---
title: "ausvotesTR Examples"
author: "Damon Muller"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ausvotesTR Examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Undisclosed ('dark') funding in Australia

The following code replicated the analysis used in [_Undisclosed funding sources in Australian federal politics: a quick guide_](https://parlinfo.aph.gov.au/parlInfo/download/library/prspub/7248350/upload_binary/7248350.pdf;fileType=application/pdf).

## Figure 1: Total reported receipts by type (federal)

```{r receipts_by_type}
library(ausvotesTR)
library(dplyr)
library(tidyr)
library(ggplot2)
library(scales)

Receipts_by_type <- returns_party %>%
  group_by(FinancialYear) %>% 
  summarise(TotalReceipts = sum(TotalReceipts)) %>% 
  left_join(returns_receipts_details %>% 
              filter(ReturnTypeDescription == "Political Party Return") %>% 
              mutate(ReceiptType = ifelse(ReceiptType == "", "Unspecified", ReceiptType),
                     ReceiptType = ifelse(grepl("Electoral Commission", ReceivedFromClientName, fixed = TRUE), "Public Funding", ReceiptType)) %>% 
              group_by(FinancialYear, ReceiptType) %>% 
              summarise(Amount = sum(Amount, na.rm = TRUE)) %>% 
              bind_rows(group_by(., FinancialYear) %>% 
                          summarise(Amount = sum(Amount, na.rm = TRUE)) %>% 
                          mutate(ReceiptType = "TotalDeclared")) %>%
              spread(ReceiptType, Amount, fill = 0),
            by = "FinancialYear") %>%
  mutate(Undeclared = TotalReceipts - TotalDeclared) %>% 
  gather(ReceiptType, Amount, -FinancialYear) %>%
  filter(!ReceiptType %in% c("TotalReceipts", "TotalDeclared"))

ggplot(Receipts_by_type, aes(x = FinancialYear, y = Amount, fill = ReceiptType)) +
  geom_bar(stat = "identity") + 
  scale_y_continuous(name = "Amount ($)", labels = comma) +
  scale_x_discrete(name = "Financial year (election years in red)") +
  scale_fill_discrete(name = "Receipt type") +
  ggtitle(label = "Total receipts by type") +
  theme(axis.text = element_text(angle = 45, hjust = 1, size = 12),
        axis.text.x = element_text(colour = ifelse(Receipts_by_type$FinancialYear %in% c("2018-19", "2015-16", "2013-14", "2010-11", "2007-08", "2004-05", "2001-02", "1998-99"), "red", "black")))

```

## Table 1: Reported and unreported income by party in 2018–19

```{r results='asis'}
Receipts_by_type %>% 
  spread(ReceiptType, Amount) %>% 
  knitr::kable()
```


## Declared and undeclared donations by party group, 2018-19.

```{r results='asis'}
returns_party %>% 
  mutate(PartyGroupName = ifelse(is.na(PartyGroupName), "Others", PartyGroupName)) %>% 
  mutate(PartyGroupName = ifelse(PartyGroupName %in% c("Christian Democratic Party (Fred Nile Group)", 
                                                       "Democratic Labor Party"), 
                                 "Others", 
                                 PartyGroupName)) %>% 
  group_by(FinancialYear, PartyGroupName) %>% 
  summarise(TotalReceipts = sum(TotalReceipts),
            Declared = sum(DetailsOfReceiptsTotal)) %>% 
  mutate(Undeclared = TotalReceipts - Declared) %>% 
  # select(-TotalReceipts) %>% 
  filter(FinancialYear == "2018-19") %>% 
  knitr::kable()
```

## Table 2: Donor returns donations below the disclosure threshold, 2006–19

```{r results='asis'}
returns_donor_details %>% 
  left_join(disclosure_threshold(), by = "FinancialYear") %>% 
  filter(Amount < ReportingThreshold) %>% 
  group_by(FinancialYear) %>% 
  summarise(BelowThreshold = sum(Amount, na.rm = TRUE)) %>% 
  left_join(returns_donor_details %>% 
              group_by(FinancialYear) %>% 
              summarise(Total = sum(Amount, na.rm = TRUE)),
            by = "FinancialYear") %>% 
  mutate(Percent = BelowThreshold / Total * 100) %>% 
  left_join(disclosure_threshold(), by = "FinancialYear") %>% 
  knitr::kable()
```

## Number of donors 

```{r results='asis'}
returns_donor_details %>% 
  group_by(FinancialYear, RegistrationCode, DonationMadeToClientFileId) %>% 
  summarise(Total = sum(Amount, na.rm = TRUE)) %>% 
  left_join(disclosure_threshold(), by = "FinancialYear") %>%
  filter(Total < ReportingThreshold) %>% 
  group_by(FinancialYear, ReportingThreshold) %>% 
  summarise(n = n()) %>% 
  arrange(desc(ReportingThreshold)) %>% 
  knitr::kable()
```

## Donations in Queensland (req ausvotesTR > 0.1.0)

```{r results='asis'}
tmp_qld <- returns_receipts_details %>% 
  filter(FinancialYear == "2018-19" & 
           RecipientClientId %in% returns_party$ClientFileId[returns_party$FinancialYear == "2018-19" & returns_party$State == "QLD"] & 
           ReceiptType == "Donation Received")

dim(tmp_qld)[1]
sum(tmp_qld$Amount)

```

# Search many donors at once

This can also be done with `lapply()`, but the `purrr` functions are a bit
less wordy. 

```{r search_mutliple_donors, message=TRUE, warning=FALSE, paged.print=TRUE}
library(purrr)

check_donors <- c('Rinehart', 'Hancock', 'Forrest', 'Fortescue',
                  'Pratt', 'Shimao', 'Wing Mau', 'Cannon-Brookes',
                  'Atlassian', 'Farquhar', 'Triguboff', 'Meriton',
                  'Palmer', 'Mineralogy', 'Lowy', 'Westfield',
                  'Stokes', 'Seven', 'John Gandel', 'Vicinity', 'Alan Wilson',
                  'Reece', 'Packer', 'Crown', 'Sehgal', 'Samvardhana',
                  'Chak Wing', 'Kingold', 'Glasenberg', 'Glencore',
                  'Cowin', 'Competitive Foods', 'Ainsworth', 
                  'Aristocrat', 'Lang Walker', 'Walker Group', 
                  'Richard White', 'WiseTech')

map_dfr(check_donors, search_returns, donor_only = FALSE) %>% 
  head()
```

# Aggregated donors to one party

Adds a link which allows that donor's details to be checked on the AEC website.

```{r donors_to_party, warning=FALSE, results='asis'}
library(dplyr)

returns_receipts_details %>%
  filter(PartyGroupName == "The Greens") %>% 
  filter(ReceiptType == "Donation Received") %>% 
  filter(FinancialYear %in% c('2019-20', '2018-19', '2017-18')) %>% 
  group_by(FinancialYear, ReceivedFromClientId, ReceivedFromClientName) %>% 
  summarise(Amount = sum(Amount, na.rm = TRUE)) %>% 
  mutate(link = paste0('https://transparency.aec.gov.au/AnnualClientEntity/EntityDetail?clientFileId=', ReceivedFromClientId)) %>% 
  head() %>% 
  knitr::kable()
```

